A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-21 paper/ms.tex
update ms

The presence of this additional scatter prevents a clear detection of
the RM effect.  The reason can be understood through a
model-comparison analysis.  If we compare the model with a quadratic trend and
the RM effect (Figure~\ref{fig:obliquity}) against a model with a
linear trend and the RM effect, or even a model with no RM effect at
all, then the usual goodness of fit diagnostics are as follows.
% from logs/rm_freejitter.log
\begin{align}
  \chi^2_{\rm red} &= 1.45 \quad ({\rm Quadratic+RM}) \nonumber \\
  \chi^2_{\rm red} &= 1.37 \quad ({\rm Linear+RM}) \nonumber \\
  \chi^2_{\rm red} &= 1.22 \quad ({\rm Only\ Quadratic}),
\end{align}
and
\begin{align}
  {\rm BIC} &= 251.7  \quad ({\rm Quadratic+RM}) \nonumber \\
  {\rm BIC} &= 257.7  \quad ({\rm Linear+RM}) \nonumber \\
  {\rm BIC} &= 242.8  \quad ({\rm Only\ Quadratic}).
\end{align}
The ``only quadratic'' model does well in these metrics
because it can inflate the jitter term to account for any additional
scatter during the transit.  However, we cannot justify a physical
prior on the jitter term, because we do not understand the origin of
the exposure-to-exposure scatter.  As noted above, the velocity
deviations from starspots are expected to have contributions at the
stellar rotation frequency, or harmonics thereof.  This jitter is
present on the exposure timescale (15 minutes), which is only 0.4\% of
the stellar rotation period; it is not obvious that starspots could be
the culprit.

>>>>

The presence of this additional scatter prevents a clear detection of
the RM effect.  The reason can be understood through a
model-comparison analysis.  If we compare the model with a quadratic trend and
the RM effect (Figure~\ref{fig:obliquity}) against a model with a
linear trend and the RM effect, or even a model with no RM effect at
all, then the respective Bayesian Information Criterion (BIC) values
are as follows.
% from logs/rm_freejitter.log
% \begin{align}
%   \chi^2_{\rm red} &= 1.45 \quad ({\rm Quadratic+RM}) \nonumber \\
%   \chi^2_{\rm red} &= 1.37 \quad ({\rm Linear+RM}) \nonumber \\
%   \chi^2_{\rm red} &= 1.22 \quad ({\rm Only\ Quadratic}),
% \end{align}
% and
\begin{align}
  {\rm BIC} &= 251.7  \quad ({\rm Quadratic+RM}) \nonumber \\
  {\rm BIC} &= 257.7  \quad ({\rm Linear+RM}) \nonumber \\
  {\rm BIC} &= 242.8  \quad ({\rm Only\ Quadratic}).
\end{align}
There is therefore no evidence to prefer the model with the RM effect
against a model that only accounts for the stellar variability.
The ``only quadratic'' model does particularly well because it can
inflate the jitter term to account for any additional scatter during
the transit, and it has fewer free parameters.  However, we cannot
justify a physical prior on the jitter term, because we do not
understand the origin of the exposure-to-exposure scatter.  As noted
above, the velocity deviations from starspots are expected to have
contributions at the stellar rotation frequency, or harmonics thereof.
This jitter is present on the exposure timescale (15 minutes), which
is only 0.4\% of the stellar rotation period; it is not obvious that
starspots could be the culprit.
